Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-05-31 inc/photocathode/setup/setup.tex
tweak photocathode setup

To address this need, I have experimented with many candidate photocathodes, which implement a variety of different photoemission processes.
In this chapter, I will present an example of several of these different processes, discuss its prospects for reducing the transverse emittance and finally assess its utility as an electron source for UEM.
I will then outline some future research directions that the group at UIC will continue to pursue.
Since this is the most active current field in our group's reseach, some very new results are presented near the end of the chapter and future plans are evolving.

>>>>

To address this need, I have experimented with many candidate photocathodes, which implement a variety of different photoemission processes.
In this chapter, I will present an example of several of these different processes, discuss its prospects for reducing the transverse emittance and finally assess its utility as an electron source for UEM.
I will then outline some future research directions that the group at UIC will continue to pursue.
Since this is the most active current field in our group's research, indeed some very new results are presented near the end of the chapter, future plans are continuously evolving.
